Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Latest and greatest

\begin{figure}
\begin{code}
\verbatiminput{cs.cxl}
\end{code}
\caption{A barebones critical section.}
\label{fig:cs}
\end{figure}

@@

Figure~\ref{fig:cs} shows the code.
The assertion also makes use of the method \texttt{nametag()} that
returns the name tag of the current process.
If you run the code through CXL, the assertion should fail because
there is no code yet for entering and exiting the critical section.

@@

% from any state some process should be able to eventually enter the
% critical section.  Without the help of any processes that reach ncs
% (but don't start there).

>>>>

\begin{figure}
\begin{code}
\verbatiminput{csbarebones.cxl}
\end{code}
\caption{A barebones critical section.}
\label{fig:csbarebones}
\end{figure}

\begin{figure}
\begin{code}
\verbatiminput{cs.cxl}
\end{code}
\caption{CXL model of a critical section.}
\label{fig:cs}
\end{figure}

@@

Figure~\ref{fig:csbarebones} shows the code.
The assertion also makes use of the method \texttt{nametag()} that
returns the name tag of the current process.
If you run the code through CXL, the assertion should fail because
there is no code yet for entering and exiting the critical section.

@@

In order to detect violations of progress, and other liveness problems in
algorithms in general, CXL requires that every execution must be
able to reach a state in which all processes have terminated.
Clearly, even if mutual exclusion holds in Figure~\ref{fig:csbarebones},
the spawned processes never terminate.  In order to resolve this, we
will model processes in critical regions using the framework in
Figure~\ref{fig:cs}: a process can \emph{choose} to enter a
critical region more than once, but it can also choose to terminate, even
without entering the critical region ever.
Note also that we have dropped the \texttt{@ncs} label: it would serve no
specific purpose.

\begin{quote}
Try it out!
\begin{itemize}
\item Plug \texttt{while True: pass;;} for entering the critical region
in Figure~\ref{fig:cs} and run CXL.  It should print a trace
to a state from which a terminating state cannot be reached.
\end{itemize}
\end{quote}
